### 2016-11-28 README.Rmd
minor tweaks

In this example, we fit a random forest to the Boston housing data. Note, for any of the following examples, you can see a progress bar by simply specifying `.progress = "text"` in the call to `partial`. You may also reduce the computation time via the `grid.resolution` option in the call to `partial`.
```{r, message = FALSE, warning=FALSE}
# Load required packages
library(ggmap)  # for plotting data on maps
library(pdp)  # for constructing PDPs
library(randomForest)  # for random forest algorithm

@@

In this example, we fit another random forest to the Pima Indians diabetes data.
```{r, message=FALSE, warning=FALSE}
# Fit a random forest to the Pima Indians diabetes data
data (pima)  # load the boston housing data
set.seed(102)  # for reproducibility
pima.rf <- randomForest(diabetes ~ ., data = pima, na.action = na.omit)

# Partial dependence of glucose on diabetes test result (neg/pos)
partial(pima.rf, pred.var = c("glucose", "age"), plot = TRUE, chull = TRUE)
```

@@

Finally, we demonstrate the seamless interface between the `pdp` package and the `caret` package; `caret` is an extremetly useful package for classification and regression training that, essentially, has one function (`train`) for fitting all kinds of predictive models in R (e.g., `glmnet`, `svm`, `xgboost`, etc.). For illustration we use `caret`'s `train` function to tune a support vector machine (SVM) with a radial basis function kernel to the Pima Indians diabetes data. We then construct PDPs from the final model for the most "important" variables. When training a model using `caret`'s `train` function, you can view tuning progress by setting `verboseIter = TRUE` in the call to `trainControl`.
```{r, message=FALSE, warning=FALSE}
# Load required packages
library(caret)  # for model training/tuning

@@

# Partial dependence of glucose on diabetes test result (neg/pos)
partial(pima.svm, pred.var = "glucose", plot = TRUE, rug = TRUE)
```

>>>>

In this example, we fit a random forest to the Boston housing data. (See `?boston` for a brief explanation of the data.) Note, for any of the following examples, you can see a progress bar by simply specifying `.progress = "text"` in the call to `partial`. You may also reduce the computation time via the `grid.resolution` option in the call to `partial`.
```{r, message = FALSE, warning=FALSE}
# Load required packages
library(ggmap)  # for plotting data on maps
library(pdp)  # for constructing PDPs
library(randomForest)  # for random forest algorithm

@@

In this example, we fit a random forest to the Pima Indians diabetes data. (See `?pima` for a brief explanation of the data.)
```{r, message=FALSE, warning=FALSE}
# Fit a random forest to the Pima Indians diabetes data
data (pima)  # load the boston housing data
set.seed(102)  # for reproducibility
pima.rf <- randomForest(diabetes ~ ., data = pima, na.action = na.omit)

# Partial dependence of glucose on diabetes test result (neg/pos). This may take
# a couple minutes!
partial(pima.rf, pred.var = c("glucose", "age"), plot = TRUE, chull = TRUE)
```

@@

Finally, we demonstrate the construction of PDPs from models fit using the `caret` package; `caret` is an extremetly useful package for classification and regression training that, essentially, has one function (`train`) for fitting all kinds of predictive models in R (e.g., `glmnet`, `svm`, `xgboost`, etc.).

For illustration we use `caret`'s `train` function to tune a support vector machine (SVM) with a radial basis function kernel to the Pima Indians diabetes data using 5-fold cross-validation. We then use the final model to construct a PDPs for `glucose` and `age`. Note, when training a model using `caret`'s `train` function, you can view tuning progress by setting `verboseIter = TRUE` in the call to `trainControl`.
```{r, message=FALSE, warning=FALSE}
# Load required packages
library(caret)  # for model training/tuning

@@

# Partial dependence of glucose on diabetes test result (neg/pos)
partial(pima.svm, pred.var = "glucose", plot = TRUE, rug = TRUE)

# Partial dependence of age on diabetes test result (neg/pos)
partial(pima.svm, pred.var = "age", plot = TRUE, rug = TRUE)

# Partial dependence of glucose and age on diabetes test result (neg/pos). This
# may take a couple minutes!
partial(pima.svm, pred.var = c("glucose", "age"), plot = TRUE, chull = TRUE,
        train = pima)
```
